---
title: "HW4-ADA"
output:
  pdf_document: default
  html_notebook: default
---
#                             Jing Qian (jq2282)

<br>

##### 1.a. Complete the table.
From the description, we have $a=2,\ b=3,\ n=3$. So the table is as following:

| Source | df | SS | MS | F |
|----------------|-----------------------------------------------------------------------|---------------------------------------------------------|-------------------------------------|-------------------------------------|
| Popper (A) | 1 | 4.5 | 4.5 | 32.374 |
| Corn (B) | 2 | 15.75  | 7.875 | 56.655 |
| Interaction (A*B) | 2 | 0.08 | 0.04 | 0.288 |
| Error | 12 | 1.67 | 0.139 | 1 |
| Total | 17 | 22.00 |

##### 1.b. Test H0 : No interaction against H1 : there is an interaction, use $\alpha$ = 0.05.
If $F=\frac{MSAB}{MSE}>F_{\alpha}((a-1)(b-1), ab(n-1))$, we could reject $H_0$.
```{r}
qf(1-0.05, df1=2, df2=12)
```
From above, $F=0.288$ while $F_{0.05}(2,12) = 3.885,\ F<F_{0.05}(2,12)$. 
So we could not reject $H_0$ and there is no interaction.

<br>

##### 1.c/d. Complete the table.
| Source | df | SS | MS | F |
|----------------|-----------------------------------------------------------------------|---------------------------------------------------------|-------------------------------------|-------------------------------------|
| Popper (A) | 1 | 4.5 | 4.5 | 36 |
| Corn (B) | 2 | 15.75  | 7.875 | 63 |
| Error | 14 | 1.75 | 0.125 | 1 |
| Total | 17 | 22.00 |

<br>

##### 1.e. Test H0 : No popper effect against H1 : there is a popper effect. use $\alpha$ = 0.05.
Since there is no interaction between A and B, 
if $F=\frac{MSA}{MSE}>F_{\alpha}(1, 14)$, we could reject $H_0$.
From above, $F=36$ while $F_{0.05}(1,14) = 4.6,\ F>F_{0.05}(1, 14)$. 
So we could reject $H_0$ and conclude that there is a popper effect.

<br>

##### 1.f. Test H0 : No corn effect against H1 : there is a corn effect. use $\alpha$ = 0.05.
Since there is no interaction between A and B, 
if $F=\frac{MSB}{MSE}>F_{\alpha}(2, 14)$, we could reject $H_0$.
From above, $F=63$ while $F_{0.05}(2,14) = 3.74,\ F>F_{0.05}(2, 14)$. 
So we could reject $H_0$ and conclude that there is a corn effect.

<br>

##### 2.a. Construct an interaction plot.
```{r}
data<-read.csv('~/Desktop/AdvancedDA/HW/HW4/HW4DATA.csv', header=TRUE)
interaction.plot(data$fertilizer,data$Wheat,data$response)
```
From the interaction plot above, we could see that the four lines seem to be parallel which suggests that there is no interaction between fertilizer type and wheat type.

<br>

##### 2.b. Test H0 : No interaction against H1 : there is an interaction, use $\alpha$ = 0.05.
```{r}
summary(aov(data$response~data$fertilizer*data$Wheat))
```
In the above ANOVA table, we could see that Pr(>F) for interaction is 0.902, which is larger than $\alpha=0.05$. 
So we could not reject $H_0$ and there is no interaction between fertilizer and wheat effects.

<br>

##### 2.c. Fit a model without an interaction and test H0 : No fertilizer effect against H1 : there is a fertilizer effect. Use $\alpha$ = 0.05 if you reject H0, use Tukey’s method to do pairwise comparisons of the different fertilizer types.
```{r}
summary(aov(data$response~data$fertilizer+data$Wheat))
```
From the above ANOVA table for model without interactions, we could see that Pr(>F) for fertilizer is 4.59e-07, which is smaller than $\alpha=0.05$.
So we could reject $H_0$ and there is a fertilizer effect.
```{r}
fit<-aov(data$response~data$fertilizer+data$Wheat)
TukeyHSD(fit, "data$fertilizer")
```
In the above, we use Tukey's method to do pairwise comparisons of different fertilizer types. 
We could see that the 95% confidence interval for B-A is [1.277484, 2.272516], which doesn't cover 0. 
So there is fertilizer effect and fertilizer B leads to more yields than A.

<br>

##### 2.d. Test H0 : No wheat effect against H1 : there is a wheat effect. Use $\alpha$ = 0.05 if you reject H0, use Tukey’s method to do pairwise comparisons of the different wheat types.
From the ANOVA table in 2.c., we could find that Pr(>F) for wheat is 1.97e-11, which is smaller than $\alpha=0.05$.
So we could reject $H_0$ and there is a wheat effect.
```{r}
TukeyHSD(fit, "data$Wheat")
```
Using Tukey’s method to do pairwise comparisons of the different wheat types, we could find that M is a separate group which has lower yields than N, O and P.
It is impossible to set up consistent groups for N, O and P: O and N are not significantly different; P and N are not significantly different; but P has lower yields than O.





