---
title: '5291'
name: 'Yingdi Li(yl3990), Jing Qian(jq2282), Han Gao(hg2474)'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Step1. Import data
```{r}
library(readxl)
data<-read_xlsx("NHANES Dataset Smoking.xlsx")
#View(data)
colnames(data)
```
The National Health and Nutrition Survey (NHANES3.DAT) contains 17030 observations and 16 variables. 
(delete)SDPPSU6: Pseudo-PSU: 1, 2.
(delete)SDPSTRA6: Pseudo-stratum: 01-49
(delete)WTPFHX6: Statistical weight: 225.93-139744.9
HSAGEIR: Age: years
HSSEX: Sex: 0=Female, 1=Male
DMARACER: Race: 1=White, 2=Black, 3=Other.
BMPWTLBS: Body Weight: pounds
BMPHTIN: Standing Height: inches
(delete)PEPMNK1R: Average Systolic BP: mm Hg
PEPMNK5R: Average Diastolic BP: mm Hg
(delete)HAR1: Has repondent smoked > 100 cigarettes in life: 1=Yes, 2=No
(delete)HAR3: Does respondent smoke cigarettes now: 1=Yes, 2=No
SMOKE: Smoking: 1=if HAR1=2, 2=if HAR1=1&HAR3=2, 3=if HAR1=1&HAR3=1
TCP: Serum Cholesterol: mg/100 ml
HBP: High Blood Pressure: 0 if PEPMNK1R <=140, 1 if PEPMNK1R > 140

```{r}
data<-data[-dim(data)[1],]
data<-data[,-c(1,2,3,4,13,14)]
data<-na.omit(data)
#View(data)
```

```{r}
#png("fig/SBP-DBP.png",width = 480, height = 400, units = "px")
plot(data[data$HBP==0,]$PEPMNK1R, data[data$HBP==0,]$PEPMNK5R,col = "#92C5DE" ,xlim=c(60,250), ylim=c(10,150),xlab='Average Systolic BP (mm Hg)', ylab='Average Diastolic BP (mm Hg)', main='Diastolic BP vs. Systolic BP')
points(data[data$HBP==1,]$PEPMNK1R, data[data$HBP==1,]$PEPMNK5R,col = "#FF9999", pch="x")
abline(v=140, lwd=3, lty=2)
legend(60,150,legend=c("HBP","No HBP"), col=c("#FF9999","#92C5DE"), pch=c("x","o"), ncol=1)
#dev.off()
```


## EDA

```{r}
print(cor(data$PEPMNK1R, data$PEPMNK5R))
```


```{r}
library(RColorBrewer)
par(mfrow=c(2,2))
barplot(table(data$HBP), main = "High Blood Pressure", names.arg = c("No","Yes"), col = "#92C5DE")
barplot(table(data$HSSEX), main="Barplot of Sex", names.arg = c("Female","Male"),col = brewer.pal(n = 2, name = "RdBu"))
barplot(table(data$DMARACER), main="Barplot of Race",names.arg = c("White","Black","Other"),col = brewer.pal(n = 3, name = "RdBu"))
barplot(table(data$SMOKE), main="Barplot of Smoke", names.arg = gsub("\\s","\n",c("Never Smoked","Quit Smoking","Still Smoking")),col = brewer.pal(n = 3, name = "RdBu"))

par(mfrow=c(2,2))
boxplot(data$HSAGEIR, main="Boxplot of Age",col = brewer.pal(n = 2, name = "RdBu"))
boxplot(data$BMPWTLBS, main="Boxplot of Weight",col = brewer.pal(n = 2, name = "RdBu"))
boxplot(data$BMPHTIN, main="Boxplot of Height",col = brewer.pal(n = 2, name = "RdBu"))
boxplot(data$TCP, main="Boxplot of TCP",col = brewer.pal(n = 2, name = "RdBu"))

summary(data$HSAGEIR)
summary(data$BMPWTLBS)
summary(data$BMPHTIN)
summary(data$TCP)

```


```{r}
HBP<-data$HBP
age<-data$HSAGEIR
sex<-as.factor(data$HSSEX)
race<-as.factor(data$DMARACER)
smoke<-as.factor(data$SMOKE)
weight<-data$BMPWTLBS
height<-data$BMPHTIN
chole<-data$TCP
```

## Model Selection

### 1. Full model without interaction
```{r}
fit<-glm(HBP~age+sex+race+weight+height+smoke+chole,family=binomial("logit"))
summary(fit)
```

### 2. Test whether race and smoke are significant

```{r}
fit1<-glm(HBP~age+sex+weight+height+chole,family=binomial("logit"))
anova(fit1,fit)
```

```{r}
qchisq(0.95,4)
```

**Reject the null and keep the full model.**

#### Test whether smoke is significant

```{r}
fit1<-glm(HBP~age+sex+race+weight+height+chole,family=binomial("logit"))
anova(fit1,fit)
```

```{r}
qchisq(0.95,2)
```

**Reject the null and keep the full model (with smoke).**

#### Test whether race is significant

```{r}
fit1<-glm(HBP~age+sex+weight+height+smoke+chole,family=binomial("logit"))
anova(fit1,fit)
```

```{r}
qchisq(0.95,2)
```

**Reject the null and keep the full model (with race).**


### 3. Now consider the interaction term.
```{r}
fit<-glm(HBP~age+sex+race+weight+height+smoke+chole+sex*race+sex*smoke,family=binomial("logit"))
summary(fit)
```

### test whether interactions between sex and smoke, race and smoke are significant
```{r}
fit0<-glm(HBP~age+sex+race+weight+height+smoke+chole,family=binomial("logit"))
anova(fit0,fit)
```
```{r}
qchisq(0.95,4)
```
**Reject null and keep full.**

#### test whether interactions between race and sex is significant
```{r}
fit1<-glm(HBP~age+sex+race+weight+height+smoke+chole+sex*smoke,family=binomial("logit"))
anova(fit1,fit)
```

```{r}
qchisq(0.95,2)
```

**Don't reject the null and choose fit1 (without race \* sex).**

### test whether interaction between sex and smoke is significant

```{r}
anova(fit0,fit1)
```

```{r}
qchisq(0.95,2)
```
**Reject the null, so the interaction between sex and smoke is significant.**

## 3. Model selected
The interaction between sex and smoke is significant, then we treat it as one factor with sex levels.

```{r}
f1<-ifelse(data$HSSEX==0&data$SMOKE==1,1,0)
f2<-ifelse(data$HSSEX==0&data$SMOKE==2,1,0)
f3<-ifelse(data$HSSEX==0&data$SMOKE==3,1,0)
m1<-ifelse(data$HSSEX==1&data$SMOKE==1,1,0)
m2<-ifelse(data$HSSEX==1&data$SMOKE==2,1,0)
m3<-ifelse(data$HSSEX==1&data$SMOKE==3,1,0)
```


```{r}
fit<-glm(HBP~age+race+weight+height+chole+f2+f3+m1+m2+m3,family=binomial("logit"))
summary(fit)
```

### test whether the factor (sex\*smoke) are significant

```{r}
fit1<-glm(HBP~age+race+weight+height+chole,family=binomial("logit"))
anova(fit1,fit)
```

```{r}
qchisq(0.95,5)
```

## Final model.
```{r}
summary(fit)
```

### Calculate estimated parameters.
```{r}
exp(fit$coefficients)
```


### Calculate the confidence interval
```{r}
exp(confint(fit))
```



