---
title: "Challenge Problem 1_simplified"
output: html_notebook
---
# 结构：

## 1. summary
 (goal of problem, results of analysis)
The goal of the project is the result showing....

## 2. introduction
description of the data and why is the analysis is important for the client
( describe problem: repeat description of data with own words.)

## 3. results
what results did the analysis produce and how do you interpret those results
* 不要write models, 要words。interaction? factor? concluion?

## 4. conclusion
what is the significance of your results, what is the answer to the research question

synthesize  the material we covered. It is not a regular Homework and it  should be treated differently.  
You will present your  analysis in a report of **no more that 2 pages (both sides)** . 
You should explain what you did using simple words (just like in the challenge problems). 
You do not need to explain the terminology in details. No formulas.  

* story: unbanlanced, 2 variables.





# Description from pdf
Experiment to determine the effects on yield (Y) of a crop by two factors:
fertilizer type (FERT) and level of fertilizer application (LEV).

\# FERT = 3 (1,2,3)

\# LEV = 5 (1,2,3,4,5). =1时没有肥料；2，3，4，5分别是100,200,300,400 pounds/acre.

CR design

**Problem:**
Propose an analysis strategy for analyzing the effects of these two factors. In light of the fact that each (LEV, FERT) combination in the set {(1,1),(1,2),(1,3)} represents the same experimental condition.
Bear in mmind that the usual comparisons of all levels of each factor (one at a time) are of interests, as well as information regarding interaction of the two factors.


```{r}
Y<-c(10.1,12.2,15.1,16.2,16.9,15.8,13.2,10.5,13.6,14.4,15.5,15.6,13.8,11.0,9.4,11.1,12.4,13.0,10.8)
FERT<-factor(c(rep(1,7),rep(2,6),rep(3,6)))
LEV<-factor(c(1,1,2,3,3,4,5,1,2,2,3,4,5,1,1,2,3,4,5))
data<-data.frame(FERT,LEV,Y)
print(data)
```
```{r}
interaction.plot(FERT, LEV, Y)
```

```{r}
model<-lm(Y~FERT*LEV, contrasts=list(FERT=contr.sum,LEV=contr.sum))
summary(model)
```
could ignore all interactions
```{r}
library(car)
Anova(lm( Y ~ FERT * LEV),type=2)
```

```{r}
Anova(lm(Y~FERT+LEV))
```
```{r}
summary(aov(lm(Y~FERT+LEV)))
```

```{r}
#fit<-Anova(lm(Y~FERT+LEV))
tk<-TukeyHSD(aov(Y~FERT+LEV),"FERT")
plot(tk)
```
```{r}
tk<-TukeyHSD(aov(Y~LEV+FERT),"FERT")
plot(tk)
```

```{r}
tk2<-TukeyHSD(aov(Y~FERT+LEV),"LEV")
tk2
#plot(tk2)
```

```{r}
tk2<-TukeyHSD(aov(Y~LEV+FERT),"LEV")
plot(tk2)
```

```{r}

```

