---
title: "HW3-ADA-jq2292"
output: html_notebook
---
##### Jing Qian (jq2282)

<br>

##### 1.a. Compute 95% simultaneous confidence intervals for the differences in response between the four different diets using the Bonferroni method.
```{r}
library(gdata)
data = read.xls("~/Desktop/4291-AdvancedDA/HW/HW2/HW2(Diets).xlsx", header=TRUE)
```
The 95% simultaneous confidence intervals for the differences in response between the four different diets using the Bonferroni method is:

$\overline{Y_{i\cdot}} - \overline{Y_{j\cdot}} \pm t_{\frac{\gamma}{2g}}(n-k)\ SE(\overline{Y_{i\cdot}} - \overline{Y_{j\cdot}})$.

Here $g = {k\choose2} = 6$, $t_{\frac{\gamma}{2g}}(n-k) = t_{\frac{0.05}{2*6}}(29-4) = t_{\frac{0.05}{12}}(25)$.

$SE(\overline{Y_{i\cdot}} - \overline{Y_{j\cdot}}) = \sqrt{MSE}\sqrt{\frac{1}{n_i}+\frac{1}{n_j}}$.
And we could get $MSE$ from the ANOVA table, or directly use the result of Homewok2, which is $MSE=0.039096$.

So the result is calculated using the function within loops:
$\overline{Y_{i\cdot}} - \overline{Y_{j\cdot}} \pm t_{\frac{0.05}{12}}(25)\ \sqrt{0.039096}\sqrt{\frac{1}{n_i}+\frac{1}{n_j}}$.
```{r}
CI_Bonf = function(yi, yj, MSE, n, k, g){
  Lhat = mean(yi) - mean(yj)
  t = qt(1-0.05/(2*g), n-k)
  SEL = sqrt(MSE * (1/length(yi) + 1/length(yj)))
  dev = t * SEL
  return(c(Lhat-dev, Lhat+dev))
}
for (i in 1:3){
  for (j in (i+1):4){
    cat("i =",i,", j =",j,", CI = (", CI_Bonf(data[,2][data[,1]==i], data[,2][data[,1]==j],0.039096,29,4,6),")\n")
  }
}
```

<br>

##### 1.b. Test for all pairs of factor level means whether or not they differ using the Scheffe’s procedure with α = 0.05. Set up groups of factor levels whose means do not differ.
$H_0: L = \overline{Y_{i\cdot}} - \overline{Y_{j\cdot}} = 0$.

Using the Scheffe’s procedure, if $\frac{\hat{L}^2}{\widehat{Var(\hat{L})}} > (k-1)F_{\gamma}(k-1, n-k)$, we could reject $H_0$.

Here $\widehat{Var(\hat{L})} = MSE\ \sum\limits_{i=1}^k\frac{c_i^2}{n_i} = MSE\ (\frac{1}{n_i}+\frac{1}{n_j})$, 
so we need to check whether $\frac{(\overline{Y_{i\cdot}} - \overline{Y_{j\cdot}})^2}{\frac{1}{n_i}+\frac{1}{n_j}} > (k-1)*MSE*F_{\gamma}(k-1, n-k) = (4-1)*0.039096*F_{0.05}(4-1, 29-4) = 0.3508367$.
```{r}
val = 3*0.039096*qf(1-0.05, df1=3, df2=25)
cat("Critical value is:", val,"\n")
for (i in 1:3){
  for (j in (i+1):4){
      yi = data[,2][data[,1]==i]
      yj = data[,2][data[,1]==j]
      Lhat = mean(yi) - mean(yj)
      ninv = 1/length(yi) + 1/length(yj)
      tmp = Lhat*Lhat/ninv
      if(tmp>val){
        s = "Reject H0\n"}
      else{
        s = "Accept H0\n"}
      cat("i =",i,", j =",j,", calculated value is: ",tmp,". ", s)
  }
}
```
From above result, we could see that group 1 could not differ from group 2, 3, 4. 
Group 2 could not differ from group 1 and 3, but differs from 4.
Group 3 could not differ from group 1 and 2, but differs from 4.
The results we get using the Scheffe's procedure agree with 1.(a), which is using the Bonferroni method.
From the discussion above, we could not really set up groups of factor levels here.

<br>

##### 2.a. Obtain the analysis of variance table and test whether or not the mean time lapse differs for the five agents.
```{r}
data2 = read.table("~/Desktop/4291-AdvancedDA/HW/HW3/sofdrink.txt", header=TRUE)
```
```{r}
anova(lm(data2$TimeLapse~factor(data2$Agent)))
```
Above is the ANOVA table.
From the table, we could see that the p-value is less than 2.2e-16, which is far less than $\gamma = 0.05$.
So we could reject the $H_0$ and so the mean time lapse differs for the five agents.

<br>

##### 2.b. What is the least significant difference equal to when comparing agents 1 and 5? That is, what is the value of $LSD_{15}$ when $\gamma$ = 0.05.
$LSD_{15} = t_{\frac{\gamma}{2}}(n-k)\ \sqrt{MSE}\sqrt{\frac{1}{n_1}+\frac{1}{n_5}} = t_{0.025}(95)\sqrt{7.52}\sqrt{\frac{1}{20}*2} = 1.721569$.
```{r}
t = qt(1-0.05/2, 95)
LSD15 = t*sqrt(7.52*2/20)
LSD15
```

<br>

##### 2.c. Test for all pairs of factor level means whether or not they differ using the Bonferroni procedure with γ = 0.05. Set up groups of factor levels whose means do not differ.
```{r}
pairwise.t.test(data2$TimeLapse,data2$Agent,pool.sd=TRUE,p.adjust.method="bonf")
```
From the table above, only $H_0:\mu_1 - \mu_2 = 0$ has larger p-value than $\gamma = 0.05$ so we could not reject such $H_0$.
Other pairs differ.
So we could set up groups of factor levels as: {1, 2}, {3}, {4}, {5}.

<br>

##### 2.d. Test for all pairs of factor level means whether or not they differ using the Scheffe’s procedure with γ = 0.05. Set up groups of factor levels whose means do not differ.
$H_0: L = \overline{Y_{i\cdot}} - \overline{Y_{j\cdot}} = 0$.
Similar to question 1.b., for the Scheffe's procedure, if 
$\frac{(\overline{Y_{i\cdot}} - \overline{Y_{j\cdot}})^2}{\frac{1}{n_i}+\frac{1}{n_j}} > (k-1)*MSE*F_{\gamma}(k-1, n-k) = (5-1)*7.52*F_{0.05}(5-1, 100-5) = 74.22221$, we could reject $H_0$.
```{r}
val2 = 4*7.52*qf(1-0.05, df1=4, df2=95)
cat("Critical value is:", val2,"\n")
```
```{r}
for (i in 1:4){
  for (j in (i+1):5){
      yi = data2$TimeLapse[data2$Agent==i]
      yj = data2$TimeLapse[data2$Agent==j]
      Lhat = mean(yi) - mean(yj)
      ninv = 1/length(yi) + 1/length(yj)
      tmp = Lhat*Lhat/ninv
      if(tmp>val2){
        s = "Reject H0\n"}
      else{
        s = "Accept H0\n"}
      cat("i =",i,", j =",j,", calculated value is: ",tmp,". ", s)
  }
}
```
From the result above, we could set up following groups of factor levels: {1, 2}, {3}, {4}, {5}.

<br>

##### 2.e. The marketing director wishes to compare the mean time lapses for agents 1, 3 and 5. Obtain the pairwise confidence interval for all pairwise comparisons among these three treatment means using the Bonferroni procedure with a 90% family confidence coefficient. Interpret your result.
```{r}
CI_Bonf2 = function(yi, yj, MSE, n, k, g){
  Lhat = mean(yi) - mean(yj)
  t = qt(1-0.1/(2*g), n-k)
  SEL = sqrt(MSE * (1/length(yi) + 1/length(yj)))
  dev = t  * SEL
  return(c(Lhat-dev, Lhat+dev))
}
cat("i =",1,", j =",3,", CI = (", CI_Bonf2(data2$TimeLapse[data2$Agent==1], data2$TimeLapse[data2$Agent==3],7.52,100,5,3),")\n")
cat("i =",1,", j =",5,", CI = (", CI_Bonf2(data2$TimeLapse[data2$Agent==1], data2$TimeLapse[data2$Agent==5],7.52,100,5,3),")\n")
cat("i =",3,", j =",5,", CI = (", CI_Bonf2(data2$TimeLapse[data2$Agent==3], data2$TimeLapse[data2$Agent==5],7.52,100,5,3),")\n")
```
From the pariwise comparisons among agents 1, 3 and 5, we could find that none of the confidence intervals with 90% family confidence intervals covers 0.
$H_0: \mu_1 - \mu_3 = 0$, $H_0: \mu_1 - \mu_5 = 0$ and $H_0: \mu_3 - \mu_5 = 0$ are all rejected, which means each agent belongs to a different group of factor levels.


<br>

##### 2.f. Agents 1 and 2 distribute merchandise only, agents 3 and 4 distribute cash-value coupons only and agent 5 distributes both merchandise and coupons. Estimate the contrast $L=\frac{\mu_1+\mu_2}{2}-\frac{\mu_3+\mu_4}{2}$ using a 95% confidence interval. Interpret your result.

```{r}
library(gmodels)
fit.contrast(lm(data2$TimeLapse~factor(data2$Agent)), factor(data2$Agent), c(0.5,0.5,-0.5,-0.5,0), conf=0.95)
```
We could see that the estimated 95% confidence interval is (9.057454, 11.49255), which doesn't include 0.
That means we could reject $H_0$.
So the mean of agents 1 and 2 differs from that of agents 3 and 4.
In other words, the two ways of distributions: merchandise only and cash-value coupons only have different time lapse.

<br>

##### 2.g. Estimate the following comparisons with a 95% confidence interval using the Bonferroni method $L_1 = \mu_1 − \mu_2,\ L_2 = \frac{\mu_1 + \mu_2}{2} − \mu_5,\ L_3 = \frac{μ_3 + μ_4}{2} − μ_5$.
Using the self-defined function of 95% confidence interval using the Bonferroni method, we could calculate that for each $L$.
Here the time of comparisons is 3.
MSE is 7.52, from the ANOVA table in 2.(a).
$n=100,\ k=5$.
So we have:
```{r}
g = 3
CI1 = CI_Bonf(data2$TimeLapse[data2$Agent==1], data2$TimeLapse[data2$Agent==2], 7.52, 100, 5, g)
t = qt(1-0.05/(2*g), 100-5)
MSE = 7.52
SEL2 = sqrt(MSE * (0.5*0.5*2+1)/20)
dev = t * SEL2
Lhat2 = mean((data2$TimeLapse[data2$Agent==1]+data2$TimeLapse[data2$Agent==2])/2) - mean(data2$TimeLapse[data2$Agent==5])
CI2 = c(Lhat2 - dev, Lhat2 + dev)
Lhat3 = mean((data2$TimeLapse[data2$Agent==3]+data2$TimeLapse[data2$Agent==4])/2) - mean(data2$TimeLapse[data2$Agent==5])
CI3 = c(Lhat3 - dev, Lhat3 + dev)
cat("The 95 percent confidence interval for L1 is: (", CI1,").\n")
cat("The 95 percent confidence interval for L2 is: (", CI2,").\n")
cat("The 95 percent confidence interval for L3 is: (", CI3,").\n")
```
From the calculated confidence interval, we could find that agent 1 and agent 2 could not differ.
The mean of agent 1 and agent 2 differ from agent 5.
The mean of agent 3 and agent 4 differ from agent 5.

