---
title: "HW7-ADA"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---
#                             Jing Qian (jq2282)

<br>

#### 1.a. Estimate the probability that a male, protestant and republican supports laws legalizing abortion. Estimate the probability that female, catholic and democrat supports laws legalizing abortion.
The estimated logit model is logit($\hat{\pi}$) = 0.11 + 0.16G − 0.57$R_1$ − 0.66$R_2$ + 0.47$P_1$ − 1.67$P_2$.
Then the description that a male, protestant and republican supports laws legalizing abortion corresponds to logit($\hat{\pi_1}$) = 0.11 + 0.16(0) − 0.57(1) − 0.66(0) + 0.47(0) − 1.67(1) = -2.13. 
So the probability that a male, protestant and republican supports laws legalizing abortion is 
$\hat{\pi_1} = \frac{e^{-2.13}}{1+e^{-2.13}} = 0.106$.

The description that a female, catholic and democrat supports laws legalizing abortion corresponds to logit($\hat{\pi_2}$) = 0.11 + 0.16(1) − 0.57(0) − 0.66(1) + 0.47(1) − 1.67(0) = 0.08. 
So the probability that a male, protestant and republican supports laws legalizing abortion is 
$\hat{\pi_2} = \frac{e^{0.08}}{1+e^{0.08}} = 0.520$.

<br>

#### 1.b. Interpret $b_1$ = 0.16 and $b_2$ = −0.57.
Interpretation of $b_1$ = 0.16:
If holding religion affiliation and political party fixed, the odds that a female supports laws legalizing abortion is estimated to be $e^{0.16} = 1.174$ times the odds that a male does.

Interpretation of $b_2 = -0.57$:
If holding gender and political party fixed, the odds that a protestant supports laws legalizing abortion is estimated to be $e^{-0.57} = 0.566$ times the odds that a non-protestant does.

<br>

#### 1.c. If SE($b_1$) = 0.064 construct a 95% confidence interval for $b_1$ and interpret your result.
The 95% confidence interval for $b_1$ is $b_1 \pm 1.96\ \rm{SE}(b_1) = 0.16 \pm 1.96*0.064 = [0.035, 0.285]$.

So the 95% confidence interval for $e^{b_1}$ is $[1.036, 1.330]$.
We are 95% confident that if holding religion affiliation and political party fixed, the ratio between odds that a female supports laws legalizing abortion and odds that a male does is a number between 1.036 and 1.330.

Since the 95% confidence interval for $b_1$ does not cover 0, we may infer that gender is significant to the individual's attitude towards laws legalizing abortion.

<br>

#### 1.d. Test $H_0$: $\beta_1$ = 0 against $H_a$: $\beta_1 \neq 0$.
Here we use $Z = \frac{b_1 - 0}{\rm{SE}(b_1)}$ to test hypothesis.
$Z = \frac{0.16}{0.064} = 2.5$, which is larger than $Z_{\alpha/2} = 1.96$.
So we could reject $H_0: \beta_1 = 0$ with $\alpha = 0.05$, which means that gender is a significant variable to whether an individual supports laws legalizing abortion.

<br>

#### 1.e. If SE($b_2$) = 0.38 construct a 95% confidence interval for $b_2$ and interpret your result.
The 95% confidence interval for $b_2$ is $b_2 \pm 1.96\ \rm{SE}(b_2) = -0.57 \pm 1.96*0.38 = [-1.315, 0.175]$.

So the 95% confidence interval for $e^{b_2}$ is $[0.268, 1.191]$.
We are 95% confident that if holding gender and political party fixed, the ratio between odds that a protestant supports laws legalizing abortion and odds that a non-protestant does is a number between 0.268 and 1.191.

Since the 95% confidence interval for $b_2$ covers 0, we may infer that whether an individual is protestant or not is not significant to his or her attitude towards laws legalizing abortion.

<br>

#### 1.f. Test $H_0$: $\beta_2$ = 0 against $H_a$: $\beta_2 \neq 0$.
Here we use $Z = \frac{b_2 - 0}{\rm{SE}(b_2)}$ to test hypothesis.
$Z = \frac{-0.57}{0.38} = -1.5$, whose absolute value is smaller than $Z_{\alpha/2} = 1.96$.
So we could not reject $H_0: \beta_2 = 0$ with $\alpha = 0.05$, which means that whether an individual is a protestant or not is not significant to his or her attitude towards laws legalizing abortion.

<br>

#### 2.a. Estimate $\beta_1$ and $\beta_2$ and interpret your result.
```{r}
data<-read.csv("~/Desktop/AdvancedDA/HW/HW7/adolescent.csv",header=TRUE,sep=',')
attach(data)
```
```{r}
logit1<-glm(cbind(Yes,No)~factor(Gender)+factor(Race),family=binomial)
logit1
```
Here Gender = 1 if gender is male and Gender = 0 if gender is female.
Race = 1 if race is white and Race = 0 if race is black.
Then we get estimated coefficients: $b_1 = 0.6478,\ b_2 = -1.3135$.

$b_1 = 0.6478$ means that if holding race fixed, the odds that a male adolescent has had intercourse is estimated to be $e^{0.6478} = 1.911$ times the odds that a female does.

$b_2 = -1.3135$ means that if holding gender fixed, the odds that a white adolescent has had intercourse is estimated to be $e^{-1.3135} = 0.269$ times the odds that a black does.

<br>

#### 2.b. Construct a 95% confidence interval to describe the effect of gender on the odds of Intercourse controlling for race (i.e. construct a 95% interval for $e^{\beta_1}$). Interpret your result.
```{r}
summary(logit1)
```
From the result above, SE($b_1$) = 0.2250 for $b_1 = 0.6478$.
The 95% confidence interval for $b_1$ is: $b_1 \pm 1.96\ \rm{SE}(b_1) = 0.6478 \pm 1.96*0.2250 = [0.207, 1.089]$.

So the 95% interval for $e^{b_1}$ is $[1.230, 2.971]$.
We are 95% confident that if holding race fixed, the ratio between odds that a male adolescent has had intercourse and odds that a female does is a number between 1.230 and 2.971.

Since the 95% confidence interval for $e^{b_1}$ does not cover 1, we may infer that gender is significant to having sexual intercourse.

<br>

#### 2.c. Test $H_0$: $\beta_1$ = 0 against $H_a$: $\beta_1 \neq 0$. Use $\alpha$ = 0.05.
Here we use $Z = \frac{b_1 - 0}{\rm{SE}(b_1)}$ to test hypothesis.
$Z = \frac{0.6478}{0.2250} = 2.879$, which is larger than $Z_{\alpha/2} = 1.96$.
So we could reject $H_0: \beta_1 = 0$ with $\alpha = 0.05$, which means that gender is a significant variable to whether an individual has had sexual intercourse.










