---
title: "Project Analysis_jq2282"
output: html_notebook
---
```{r}
library(readxl)
data <- read_excel("~/Desktop/AdvancedDA/Project/NHANES Dataset Smoking.xlsx")
View(data)
```
The National Health and Nutrition Survey (NHANES3.DAT) contains 17030 observations and 16 variables. 
SDPPSU6: Pseudo-PSU: 1, 2.
SDPSTRA6: Pseudo-stratum: 01-49
WTPFHX6: Statistical weight: 225.93-139744.9
HSAGEIR: Age: years
HSSEX: Sex: 0=Female, 1=Male
DMARACER: Race: 1=White, 2=Black, 3=Other.
BMPWTLBS: Body Weight: pounds
BMPHTIN: Standing Height: inches
PEPMNK1R: Average Systolic BP: mm Hg
PEPMNK5R: Average Diastolic BP: mm Hg
HAR1: Has repondent smoked > 100 cigarettes in life: 1=Yes, 2=No
HAR3: Does respondent smoke cigarettes now: 1=Yes, 2=No
SMOKE: Smoking: 1=if HAR1=2, 2=if HAR1=1&HAR3=2, 3=if HAR1=1&HAR3=1
TCP: Serum Cholesterol: mg/100 ml
HBP: High Blood Pressure: 0 if PEPMNK1R <=140, 1 if PEPMNK1R > 140

<font color='red'>Case和SEQN代表的意思是？</font>

```{r}
data_yes = data[data$HBP==1,]
data_no = data[data$HBP==0,]
cat('#records of HBP=1: ',nrow(data_yes), '. #records of HBP=0: ', nrow(data_no))
set.seed(100)
train_yes = data_yes[sample(nrow(data_yes), 10, replace=FALSE),]
View(train_yes)
```




