---
title: "Project Analysis_jq2282"
output: html_notebook
---

# 1. Data Exploration
## 1.1. Import data
```{r}
library(readxl)
data <- read_excel("~/Desktop/AdvancedDA/Project/NHANES Dataset Smoking.xlsx")
View(data)
```
The National Health and Nutrition Survey (NHANES3.DAT) contains 17030 observations and 16 variables. 
(delete)SDPPSU6: Pseudo-PSU: 1, 2.
(delete)SDPSTRA6: Pseudo-stratum: 01-49
(delete)WTPFHX6: Statistical weight: 225.93-139744.9
HSAGEIR: Age: years
HSSEX: Sex: 0=Female, 1=Male
DMARACER: Race: 1=White, 2=Black, 3=Other.
BMPWTLBS: Body Weight: pounds
BMPHTIN: Standing Height: inches
(delete)PEPMNK1R: Average Systolic BP: mm Hg
PEPMNK5R: Average Diastolic BP: mm Hg
(delete)HAR1: Has repondent smoked > 100 cigarettes in life: 1=Yes, 2=No
(delete)HAR3: Does respondent smoke cigarettes now: 1=Yes, 2=No
SMOKE: Smoking: 1=if HAR1=2, 2=if HAR1=1&HAR3=2, 3=if HAR1=1&HAR3=1
TCP: Serum Cholesterol: mg/100 ml
HBP: High Blood Pressure: 0 if PEPMNK1R <=140, 1 if PEPMNK1R > 140

**删掉这些变量**
* Case和SEQN是编号。
* SDPPSU6，SDPSTRA6和WTPFHX6与统计过程有关，删掉。
* PEPMNK1R决定了HBP，删掉。
* SMOKE由HAR1&HAR3组合形成，所以删去后二者

```{r}
# data <- na.omit(data)
# barplot(table(data$HBP))
data<-data[-dim(data)[1],]
data<-data[,-c(1,2,3,11,13,14)]
data<-na.omit(data)
#View(data)
```

```{r}
colnames(data)
```

## 1.2. Split data into training and testing
```{r}
# Create training and Test samples

data_yes = data[data$HBP==1,]
data_no = data[data$HBP==0,]
cat('#records of HBP=1: ',nrow(data_yes), '. #records of HBP=0: ', nrow(data_no))
size = nrow(data_yes)
set.seed(100)
train_yes_id = sample(size, 0.9*size, replace=FALSE)
train_no_id = sample(nrow(data_no), 0.9*size, replace=FALSE)
train_yes = data_yes[train_yes_id,]
train_no = data_no[train_no_id,]
train_data = rbind(train_yes, train_no)
print(table(train_data$HBP))

test_yes = data_yes[-train_yes_id,]
test_no = data_no[-train_no_id,]
test_data = rbind(test_yes, test_no)

table(test_data$HBP)
```

```{r}
cor(train_data$PEPMNK1R, train_data$PEPMNK5R)
```
PEPMNK1R: Average Systolic BP: mm Hg
PEPMNK5R

```{r}
summary(glm(train_data$HBP~factor(train_data$SMOKE)+train_data$PEPMNK5R,family=binomial("logit")))
```


```{r}
table(train_data$SMOKE)
```


## 1.3. Distribution plot
```{r}
library(RColorBrewer)
par(mfrow=c(1,3))
barplot(table(train_data$HSSEX), main="Barplot of Sex", names.arg = c("Female","Male"),col = brewer.pal(n = 2, name = "RdBu"))
barplot(table(train_data$DMARACER), main="Barplot of Race",names.arg = c("White","Black","Other"),col = brewer.pal(n = 3, name = "RdBu"))
barplot(table(train_data$SMOKE), main="Barplot of Smoke", names.arg = c("Never Smoked","Quit Smoking","Still Smoking"),col = brewer.pal(n = 3, name = "RdBu"))
```

```{r}
par(mfrow=c(2,2))
boxplot(train_data$HSAGEIR, main="Boxplot of Age",col = brewer.pal(n = 2, name = "RdBu"))
boxplot(train_data$BMPWTLBS, main="Boxplot of Weight",col = brewer.pal(n = 2, name = "RdBu"))
boxplot(train_data$BMPHTIN, main="Boxplot of Height",col = brewer.pal(n = 2, name = "RdBu"))
boxplot(train_data$TCP, main="Boxplot of TCP",col = brewer.pal(n = 2, name = "RdBu"))
```


