---
title: "Lec2 Non-parametric Test"
output: html_notebook
---

Load data:
```{r}
income<-c(7,1110,7.1,5.2,8,12,0,5,2.1,2,46,7.5)
summary(income)
t.test(income, mu=1)
```
明显可见1110这个outlier极大影响了95% CI for the mean.
这个t based CI是可疑的。
因此做median test更合理。

## Sign Test for a population median
Test median is 1 against the median not zero at 5% use:
```{r}
library("BSDA")
SIGN.test(income, md=1,alternative="two.sided",conf.level = 0.95)
```
可见得到的median 的CI是[2.4085, 11.5745]。比mean的结果更合理。

One sided test possible:
```{r}
SIGN.test(data, md=1,alternative="greater",conf.level = 0.95)
SIGN.test(data, md=1,alternative="less",conf.level = 0.95)
```


## Example: Age at first heart transplant
**Question of interest: ** is the typical age at first transplant 50?
```{r}
age<-c(54,42,51,54,49,56,33,58,54,64,49)
sort(age)
```
```{r}
summary(age)
```
```{r}
hist(age,breaks = 5)
```

```{r}
boxplot(age,horizontal = TRUE)
```
```{r}
library("car")
qqPlot(age)
```
<font color='red'>不懂qqplot</font>

The normal QQ-plot of the same data indicates mild deviation from normality in the left tail.

```{r}
t.test(age,mu=50)
```

```{r}
SIGN.test(age, md=50)
```

## Wilcoxon Signed Rank Test
```{r}
data<-c(20,18,23,5,14,8,18,22)
data
wilcox.test(data,mu=10,conf.int=TRUE,correct = FALSE)
```
可知W=32， 而E(W)是n(n+1)/4，这里n=8. 我们知道如果|W-n(n+1)/4|太大，就要reject H0.

## Nonparametric Analysis of Paired Data
```{r}
a<-c(0.7,-1.6,-0.2,-1.2,0.1,3.4,3.7,0.8,0.0,2.0)
b<-c(1.9,0.8,1.1,0.1,-0.1,4.4,5.5,1.6,4.6,3.0)
d<-a-b
shapiro.test(d)
```
a, b两组remedies,H0: $\mu_a = \mu_b$。
首先进行normality test, Shapiro-Wilk是常见的normality test. 
<font color='red'>具体的shapiro-wilk也不知道</font>
发现reject null hypothesis, the difference is from a normal distribution.
```{r}
wilcox.test(d, mu=0, conf.int=TRUE)
```
可见，reject H0且b比a好

### 另一个
```{r}
g1<-c(0.8,2.8,4.0,2.4,1.2,0.0,6.2,1.5,28.8,0.7)
g2<-c(2.3,0.3,5.2,3.1,1.1,0.9,2.0,0.7,1.4,0.3)
wilcox.test(g1,g2, exact=FALSE)
```
```{r}
wilcox.test(g1,g2)
```
可以发现，因为这里g1与g2 size 不同，得设成exact=FALSE, 就不会报错了。


