---
title: "Lec5"
output: html_notebook
---

# 1. Slides: Two Way ANOVA
```{r}
#prepare data
response<-c(47,43,62,68,41,39,46,40,67,71,42,46)
A<-c(rep(c(rep("A1",2),rep("A2",2),rep("A3",2)),2))
B<-c(rep("B1",6),rep("B2",6))
boxplot(response~A*B)
```
A: 3 levels <br>
B: 2 levels <br>
a=3, b=2, n=2 <br>
因为数据少，可以在x轴上把每种treatment组合展开显示。
```{r}
tapply(response, list(A), mean)
tapply(response, list(A), mean)
#tapply(x, index, function), index is factors from list
```
```{r}
interaction.plot(A,B,response)
```

实线与虚线间的差别：比如A1点上，就是compare levels of B at A1.

#### Step 1. Look at interaction first
```{r}
summary(aov(response~A*B))
```
From ANOVA table above, total # = abn = 12.
df(A) = a-1 = 2, df(B) = b-1 = 1, df(AB) = (a-1)(b-1) = 2, df(Residuals) = ab(n-1) =  6.

尽管A的p-value很小，但是**Focus on interaction first**.
这里accept no interaction. 那么interaction的df被residuals吸收。
No interaction，前面的曲线应该不交叉（平行的上下两个折线）。

#### Step 2. Model without interaction
```{r}
summary(aov(response~A+B))
```
另一方面，由于B的影响可以忽略，B1和B2应该是重叠——一条折线。由于error(randomness)，导致现在的情况。

#### Step 3. <font color=red>不确定是不是都减到一个factor</font>
```{r}
summary(aov(response~A))
```

#### Step 4. Pairwise comparisons
```{r}
fit<-aov(response~A)
tk<-TukeyHSD(fit, "A")
plot(tk)
```
```{r}
tk
```
So two groups {A1, A3} and {A2}.
We could see the group division from the plot too.
For 95% family CI, only CI of (A3-A1) covers 0. So no difference between A1 and A3.
CI for (A2-A1) positive, so A2 > A1; similarly, A3 < A2.

Family CI: joint statements 同时成立，总共的confidence 是95%. 
为了joint statement成立，必须要adjust单个的置信度。
我们现在有三个方法：Bonf, Scheffe and Tukey.


