---
title: "HW5-ADA"
output:
  pdf_document: default
  html_notebook: default
---
#                             Jing Qian (jq2282)

<br>

#### 1.a. Give the design matrix corresponding the the model $y_{ijk} = \mu+\alpha_i+\beta_j+(\alpha\beta)_{ij}+\epsilon_{ijk}$ where $\alpha_1+\alpha_2=0,\ \beta_1+\beta_2=0,\ (\alpha\beta)_{11}+(\alpha\beta)_{21}=0,\ (\alpha\beta)_{12}+(\alpha\beta)_{22}=0,\ (\alpha\beta)_{11}+(\alpha\beta)_{12}=0,\ (\alpha\beta)_{21}+(\alpha\beta)_{22}=0$.
The design matrix is as following if we define $A_i=1$ when A is High and $A_i=-1$ when A is low; $B_j=1$ when B is New and and $B_j=-1$ when B is Old:
```{r}
Y<-c(0.83, 0.78, 0.75, 0.83, 0.86, 0.67, 0.73, 0.72, 0.81, 0.85, 0.87, 0.68, 0.73, 0.74)
A<-c(rep('Low', 7), rep('High', 7))
B<-c(rep(c(rep('New', 4), rep('Old', 3)), 2))
data<-data.frame(Y, A, B)
#print(data)
```
```{r}
model.matrix(~A*B, contrasts=list(A=contr.sum, B=contr.sum))
```

<br>

#### 1.b. Construct an interaction plot. Does it suggest that there is an interaction between fertilizer type and wheat type?
```{r}
interaction.plot(A, B, Y)
```

The lines in the interaction plot are not parallel to each other, which suggests that there is interaction between fertilizer type and wheat type.

<br>

#### 1.c. Test H0 : No interaction against Ha : there is an interaction, use $\alpha$ = 0.05.
```{r}
summary(aov(Y~A*B))
```
From the ANOVA table above, we could see that p value of the test is 0.4607, which is larger than $\alpha$.
So we could not reject $H_0$ and there is no interaction between A and B.

<br>

#### 1.d. It is decided to fit a model without an interaction. Test H0 : there is no A effect against Ha : there is an A effect. Use $\alpha$ = 0.05.
```{r}
library(car)
model<-lm(Y~A+B)
Anova(model, type=3)
```
From the above ANOVA table with type III SS, we could see that the p value of the test is 0.83110, which is larger than $\alpha$. So we accept H0 and there is no A effect.

<br>

#### 1.e. It is decided to fit a model without an interaction. Test H0 : there is no B effect against Ha : there is an B effect. Use $\alpha$ = 0.05.
From the above ANOVA table with type III SS, we could see that the p value of the test is 0.05771, which is larger than $\alpha$. So we accept H0 and there is no B effect.

<br>

#### 2.a. Estimate the $\beta_i$s and interpret your result (see note for how to fit this model ) 
```{r}
y<-c(28.0,28.6,27.4,33.3,34.5,33.0,32.0,35.6,34.4,35.0,34.0,33.3,34.7,33.5,32.3,33.4,33.0,32.0,29.6,30.6,28.6,29.8)
D1<-factor(c(rep(0,3),rep(1,2),rep(0,4),rep(1,3),rep(0,3),1,rep(0,2),rep(1,2),rep(0,2)))
D2<-factor(c(rep(0,12),1,rep(0,3),rep(1,2),rep(0,2),rep(1,2)))
x1<-c(rep('A',3),rep('B',2),rep('A',4),rep('B',3),'C',rep('A',2),'B',rep('C',2),rep('B',2),rep('C',2))
x2<-c(rep(0,5),rep(1,8),rep(2,5),rep(3,4))
#data2<-data.frame(y,D1,D2,x1,x2)
#print(data2)
```

```{r}
fit2<-lm(y~D1+D2+x2)
summary(fit2)
```
When type A, the response is modelled as $Y_i = \beta_0+\beta_3x_2+\epsilon_i$; 
When type B, the response is modelled as $Y_i = \beta_0+\beta_1+\beta_3x_2+\epsilon_i$; 
When type C, the response is modelled as $Y_i = \beta_0+\beta_2+\beta_3x_2+\epsilon_i$.

From the script above, the estimated $\beta_0=32.017,\ \beta_1=1.522,\ \beta_2=0.525,\ \beta_3=-0.419$.
However, among all these $\beta_i$, only $\beta_0$ is significant while others are not.
The fitted result suggests that neither premium gasoline unleaded type (A, B, C) or amount of gasoline additive VST (0, 1, 2, 3 units) has significant contribution to the gasoline mileage obtained by an automobile called Encore.

<br>

#### 2.b. Construct a 95% confidence interval for $\beta_3$ and interpret your result

```{r}
confint(fit2,"x2",level = 0.95)
```
The 95% confidence interval for $\beta_3$ is [-1.688644, 0.8502126], which covers 0.
From the confidence interval result, we could see that amount of gasoline additive VST is not a significant variable to the gasoline mileage $y$, which agrees with the conclusion in 2.a.

<br>

#### 2.c. Test H0 :$\beta_1=\beta_2=0$ against Ha :Not H0 using $\alpha$=0.05.
```{r}
Anova(lm(y~x1+x2),type=3)
```
Since $\beta_1$ and $\beta_2$ are dummy variables for variable $x_1$, we could turn the $H_0: \beta_1=\beta_2=0$ to $H_0:$ there is no $x_1$ effect.
From the above ANOVA table with type III SS, we could see that the p value for the test is 0.4832, which is larger than $\alpha$.
So $H_0$ could not be rejected and the premium gasoline unleaded type (A, B, C) is not a significant variable, which agrees with the concluion in 2.a.



